  \item
  V.~V. Korobkin, A.~N. Sesekin, O.~L. Tashlykov, and A.~G. Chentsov, {\em Metody
    marshrutizatsii i ikh prilozheniya v zadachakh povysheniya ehffektivnosti i
    bezopasnosti ehkspluatatsii atomnykh stantsiy}.
  \newblock Izdatel'stvo "Novye tekhnologii", 2012.

  \item
  A.~G. Chentsov, ``{Dynamic programming in routing problems (nuclear power,
    Engineering)},'' {\em AIP Conference Proceedings}, vol.~2315, p.~040011, Dec
    2020.

  \item
  A.~A. Petunin, A.~G. Chentsov, and P.~A. Chentsov, {\em Optimal'naya
    marshrutizatsiya instrumenta mashin figurnoy listovoy rezki s chislovym
    programmnym upravleniem. Matematicheskie modeli i algoritmy}.
  \newblock Izdatel'stvo Ural'skogo universiteta, 2020.

  \item
  A.~G. Chentsov, P.~A. Chentsov, A.~A. Petunin, and A.~N. Sesekin, ``Model of
    megalopolises in the tool path optimisation for {CNC} plate cutting
    machines,'' {\em International Journal of Production Research}, vol.~56,
    no.~14, pp.~4819--4830, 2018.

  \item
  G.~Gutin and A.~P. Punnen, eds., {\em The traveling salesman problem and its
    variations}.
  \newblock Springer Science \& Business Media., 2006.

  \item
  W.~J. Cook, {\em In pursuit of the traveling salesman: mathematics at the
    limits of computation}.
  \newblock Princeton University Press, 2011.

  \item
  E.~K. Gimadi and M.~Y. Khachay, {\em Ehkstremal'nye zadachi na mnozhestvakh
    perestanovok}.
  \newblock Ekaterinburg: Izd-vo UMTS UPI, 2016.

  \item
  I.~I. Melamed, S.~I. Sergeev, and I.~K. Sigal, ``Zadacha kommivoyazhera.
    voprosy teorii,'' {\em Avtomatika i telemekhanika}, no.~9, pp.~3--33, 1989.

  \item
  R.~Bellman, ``Primenenie dinamicheskogo programmirovaniya k zadache o
    kommivoyazhere,'' {\em Kiberneticheskiy sbornik}, vol.~9, pp.~219--228, 1964.

  \item
  M.~Kheld and R.~Karp, ``Primenenie dinamicheskogo programmirovaniya k zadacham
    uporyadocheniya,'' {\em Kiberneticheskiy sbornik}, vol.~9, pp.~202--218,
    1964.

  \item
  A.~G. Chentsov, {\em Ehkstremal'nye zadachi marshrutizatsii i raspredeleniya
    zadaniy: voprosy teorii}.
  \newblock M.--Izhevsk: NITS ``Regulyarnaya i khaoticheskaya dinamika'',
    Izhevskiy institut komp'yuternykh issledovaniy, 2008.

  \item
  R.~Dewil, P.~Vansteenwegen, and D.~Cattrysse, {\em {Sheet Metal Laser Cutting
    Tool Path Generation: Dealing with Overlooked Problem Aspects}}, vol.~639.
  \newblock Trans Tech Publications Ltd, 2015.

  \item
  K.~A. Dowsland and W.~B. Dowsland, ``{Solution approaches to irregular nesting
    problems},'' {\em European Journal of Operational Research}, vol.~84,
    pp.~506--521, Aug 1995.

  \item
  Y.~Stoyan, A.~Pankratov, and T.~Romanova, ``{Placement Problems for Irregular
    Objects: Mathematical Modeling, Optimization and Applications},'' in {\em
    {Optimization Methods and Applications : In Honor of Ivan V. Sergienko's 80th
    Birthday}}, pp.~521--559, Cham, Switzerland: Springer, Dec 2017.

  \item
  R.~Alvarez-Vald{\'e}s, M.~A. Carravilla, and J.~F. Oliveira, ``Cutting and
    packing.,'' in {\em {Handbook of Heuristics}}, pp.~931--998, Berlin, Germany:
    Springer, Mar 2018.

  \item
  J.~S. Hoeft and U.~S. Palekar, ``Heuristics for the plate-cutting traveling
    salesman problem,'' {\em Iie Transactions}, vol.~29, pp.~719--731, 1997.

  \item
  R.~Dewil, P.~Vansteenwegen, and D.~Cattrysse, ``{A review of cutting path
    algorithms for laser cutters},'' {\em International Journal of Advanced
    Manufacturing Technology}, vol.~87, pp.~1865--1884, Nov 2016.

  \item
  R.~Dewil, P.~Vansteenwegen, D.~Cattrysse, M.~Laguna, and T.~Vossen, ``{An
    improvement heuristic framework for the laser cutting tool path problem},''
    {\em International Journal of Production Research}, vol.~53, pp.~1761--1776,
    Mar 2015.

  \item
  N.~Levichev, G.~C. Rodrigues, and J.~R. Duflou, ``Real-time monitoring of fiber
    laser cutting of thick plates by means of photodiodes,'' {\em Procedia CIRP},
    vol.~94, pp.~499--504, 2020.

  \item
  S.~Sonawane, P.~Patil, R.~Bharsakade, and P.~Gaigole, ``Optimizing tool path
    sequence of plasma cutting machine using tsp approach,'' {\em E3S Web of
    Conferences}, vol.~184, p.~01037, 01 2020.

  \item
  N.~D. Ganelina and V.~D. Frolovskiy, ``Dekompozitsionnyy metod optimizatsii
    proektirovaniya upravlyayushchikh programm teplovoy rezki metalla na
    oborudovanii s chpu,'' {\em Nauchnyy Vestnik NGTU. Novosibirsk: Izd-vo NGTU},
    no.~2, pp.~9--19, 2006.

  \item
  M.~A. Verkhoturov and P.~Y. Tarasenko, ``Matematicheskoe obespechenie zadachi
    optimizatsii puti rezhushchego instrumenta pri ploskom figurnom raskroe na
    osnove tsepnoy rezki,'' {\em Vestnik Ufimskogo gosudarstvennogo aviatsionnogo
    tekhnicheskogo universiteta}, vol.~10, no.~2, pp.~123--130, 2008.

  \item
  T.~A. Makarovskikh and A.~V. Panyukov, ``{Software for Constructing A-chains
    with Ordered Enclosing for a Plane Connected 4-regular Graph xn--The-su0aa
    work was supported by Act 211 Government of the Russian Federation, contract
    No. 02.A03.21.0011.},'' {\em IFAC-PapersOnLine}, vol.~52, pp.~2650--2655, Jan
    2019.

  \item
  T.~A. Makarovskikh, A.~V. Panyukov, and E.~A. Savitskiy, ``{Mathematical models
    and routing algorithms for economical cutting tool paths},'' {\em
    International Journal of Production Research}, vol.~56, pp.~1171--1188, Feb
    2018.

  \item
  T.~Makarovskikh, A.~Panyukov, and E.~Savitsky, ``{Software Development for
    Cutting Tool Routing Problems},'' {\em Procedia Manufacturing}, vol.~29,
    pp.~567--574, Jan 2019.

  \item
  A.~A. Petunin and P.~A. Chentsov, ``Routing in {CNC} cutting machines:
    Engineering constraints,'' {\em Acta Polytechnica Hungarica}, vol.~17,
    pp.~165--177, 2020.

  \item
  A.~Petunin, ``{General Model of Tool Path Problem for the {CNC} Sheet Cutting
    Machines},'' {\em IFAC-PapersOnLine}, vol.~52, pp.~2662--2667, Jan 2019.

  \item
  A.~A. Petunin and C.~D. Stylios, ``Optimization models of tool path problem for
    {CNC} sheet metal cutting machines,'' {\em IFAC-PapersOnLine}, vol.~49,
    pp.~23--28, 2016.

  \item
  D.~Mejia, A.~Moreno, A.~Arbelaiz, J.~Posada, O.~Ruiz-Salguero, and R.~Chopitea,
    ``{Accelerated Thermal Simulation for Three-Dimensional Interactive
    Optimization of Computer Numeric Control Sheet Metal Laser Cutting},'' {\em
    Journal of Manufacturing Science and Engineering}, vol.~140, Mar 2018.

  \item
  A.~A. Petunin, E.~G. Polyshuk, P.~A. Chentsov, S.~S. Ukolov, and V.~I. Krotov,
    ``{The termal deformation reducing in sheet metal at manufacturing parts by
    {CNC} cutting machines},'' {\em IOP Conference Series: Materials Science and
    Engineering}, vol.~613, p.~012041, Oct 2019.

  \item
  M.~Z. Lagerkvist, M.~Nordkvist, and M.~Rattfeldt, ``{Laser Cutting Path
    Planning Using CP},'' in {\em {Principles and Practice of Constraint
    Programming}}, pp.~790--804, Berlin, Germany: Springer, Sep 2013.

  \item
  H.~Makbul, T.~Viboon, J.~Chorkaew, and D.~Chaiya, ``Laser cutting path
    optimization using simulated annealing with an adaptive large neighborhood
    search,'' {\em The International Journal of Advanced Manufacturing
    Technology}, vol.~103, no.~1-4, pp.~781--792, 2019.

  \item
  M.~Balamurali, J.~N, B.~Sivaramakrishnan, and M.~Thirumoolam, ``Realization of
    effective laser blanking process by heat zone spread resistance coating and
    optimization methods,'' {\em Materials Research Express}, vol.~6, 01 2019.

  \item
  Y.~Yuan, D.~Cattaruzza, M.~Ogier, and F.~Semet, ``A branch-and-cut algorithm
    for the generalized traveling salesman problem with time windows,'' {\em
    European Journal of Operational Research}, vol.~286, no.~3, pp.~849--866,
    2020.

  \item
  M.~Khachai and E.~Neznakhina, ``Approximability of the problem about a
    minimum-weight cycle cover of a graph,'' {\em Doklady Mathematics}, vol.~91,
    no.~2, pp.~240--245, 2015.

  \item
  M.~Gendreau, G.~Ghiani, and E.~Guerriero, ``Time-dependent routing problems: A
    review,'' {\em Computers and Operations Research}, vol.~64, pp.~189--197, 07
    2015.

  \item
  J.~Kinable, A.~Cire, and W.-J. van Hoeve, ``Hybrid optimization methods for
    time-dependent sequencing problems,'' {\em European Journal of Operational
    Research}, vol.~259, pp.~887--897, 2017.

  \item
  A.~F. Alkaya and E.~Duman, ``A new generalization of the traveling salesman
    problem,'' {\em Applied and Computational Mathematics}, pp.~162--175, 2010.

  \item
  G.~Gutin and D.~Karapetyan, ``A memetic algorithm for the generalized traveling
    salesman problem,'' {\em Natural Computing}, vol.~9, no.~1, pp.~47--60, 2010.

  \item
  K.~Helsgaun, ``Solving the equality {G}eneralized {T}raveling {S}alesman
    {P}roblem using the {L}in--{K}ernighan--{H}elsgaun algorithm,'' {\em
    Mathematical Programming Computation}, pp.~1--19, 2015.

  \item
  S.~L. Smith and F.~Imeson, ``Glns: An effective large neighborhood search
    heuristic for the {G}eneralized {T}raveling {S}alesman {P}roblem,'' {\em
    Computers {\&} Operations Research}, vol.~87, pp.~1--19, 2017.

  \item
  R.~Salman, J.~S. Carlson, F.~Ekstedt, D.~Spensieri, J.~Torstensson, and
    R.~S\"{o}derberg, ``An industrially validated {CMM} inspection process with
    sequence constraints,'' {\em Procedia CIRP}, vol.~44, pp.~138 -- 143, 2016.
  \newblock 6th CIRP Conference on Assembly Technologies and Systems (CATS).

  \item
  R.~Salman, F.~Ekstedt, and P.~Damaschke, ``Branch-and-bound for the
    {P}recedence {C}onstrained {G}eneralized {T}raveling {S}alesman {P}roblem,''
    {\em Operations Research Letters}, vol.~48, no.~2, pp.~163--166, 2020.

  \item
  M.~Hajad, V.~Tangwarodomnukun, C.~Dumkum, and C.~Jaturanonda, ``Solving the
    laser cutting path problem using population-based simulated annealing with
    adaptive large neighborhood search,'' {\em Key Engineering Materials},
    vol.~833, pp.~29 -- 34, 2020.

  \item
  J.~Li, H.~Zhu, T.~Zhang, L.~He, Y.~Guan, and H.~Zhang, ``Automatic generation
    of auxiliary cutting paths based on sheet material semantic information,''
    {\em The International Journal of Advanced Manufacturing Technology},
    vol.~106, pp.~3787--3797, 2020.

  \item
  Y.~Xin, Y.~Li, W.~Li, and G.~Wang, ``Towards efficient milling of multi-cavity
    aeronautical structural parts considering aco-based optimal tool feed
    position and path,'' {\em Micromachines}, vol.~12, no.~1, 2021.

  \item
  D.~Al-Janan and T.-K. Liu, ``Path optimization of {CNC} pcb drilling using
    hybrid taguchi genetic algorithm,'' {\em Kybernetes}, vol.~45, pp.~107--125,
    01 2016.

  \item
  N.~D. Starostin and Mironov, ``Algorithm modification of the level-by-level
    approximation to the minimum route,'' in {\em 2017 IEEE International
    Symposium on Signal Processing and Information Technology (ISSPIT)},
    pp.~270--275, 2017.

  \item
  V.~A. Kandasamy and S.~Udhayakumar, ``{Effective location of micro joints and
    generation of tool path using heuristic and genetic approach for cutting
    sheet metal parts},'' {\em International Journal of Material Forming},
    vol.~13, pp.~317--329, Mar 2020.

  \item
  K.~Kuratovskiy and A.~Mostovskiy, {\em Teoriya mnozhestv}.
  \newblock M.: Mir, 1970.

  \item
  Z.~D'edonne, {\em Osnovy sovremennogo analiza}.
  \newblock M.: Mir, 1964.

  \item
  T.~Kormen, C.~Leyzerson, R.~Rivest, and K.~Shtayn, {\em Algoritmy. Postroenie i
    analiz}.
  \newblock Izdatel'skiy dom Vil'yams, 2009.

  \item
  A.~G. Chentsov and P.~A. Chentsov, ``Marshrutizatsiya v usloviyakh
    ogranicheniy: zadacha o poseshchenii megapolisov,'' {\em Avtomatika i
    telemekhanika}, no.~11, pp.~96--117, 2016.

  \item
  E.~Lawler, {\em Efficient Implementation of Dynamic Programming Algorithms for
    Sequencing Problems}.
  \newblock Report BW106, Mathematisch Centrum , Amsterdam, 1979.

  \item
  A.~Tavaeva, A.~A. Petunin, S.~Ukolov, and V.~I. Krotov, ``A cost minimizing at
    laser cutting of sheet parts on {{CNC}} machines,'' {\em Communications in
    Computer and Information Science}, vol.~10, pp.~422--437, 2019.
